### 2017-12-24 DASFAA_2018/Gruba/00-abstr.tex

\begin{abstract}
%Social media applications are emerging, with rapidly growing users and large numbers of \retd{} microblogs every minute.
The variety among massive users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model. % \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Meanwhile, building one model per user is not practical.
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our system, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests.
%, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} using datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
\end{abstract}
% behavior and activity in this paper are interchangeable

>>>>

\begin{abstract}
%Social media applications are emerging, with rapidly growing users and large numbers of \retd{} microblogs every minute.
The variety among massive users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model. % \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Meanwhile, building one model per user is not practical.
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our system, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/short-term interests and explicit/implicit interests.
%, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} using datasets of real-world social networking applications, and shown its benefits.

\keywords{user grouping \middot social networks \middot behavior modeling}
\end{abstract}
% behavior and activity in this paper are interchangeable

### 2017-12-24 DASFAA_2018/Gruba/01-intro.tex

Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users.
These users behave variously, knowledge of which is significant for various applications such as recommendation system and activity analysis.
Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.

Central to user behavior modeling is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
Already, there exist works of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

@@

\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model as in existed research.

@@

\stab(3) We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.

>>>>

\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, have attracted  massive users.
These users behave variously, knowledge of which is significant for various applications such as recommendation system and activity analysis.
Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.

Central to user behavior modeling is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
Already, there exist works of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

@@

\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of a single model for all users.

@@

\stab(3) We offer a clustering method K-Gru to deal with complex vectors, serving as an extension for standard K-Prototype algorithm.

\stab(4) We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.

### 2017-12-24 DASFAA_2018/Gruba/02-overview.tex

We consider the \retg{} behavior of users in social media.
%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.

@@

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
\end{definition}

@@

\begin{definition}
\label{def:user}
Given a user $u$, we adopt $B_u$, $R_u$ and $E_u$ to represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
\end{definition}

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
Note that $M_b.O$ is a user $u$, and $B_u$ is a set of $M_b$.

Providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower $f$ of its onwer $b.O$, i.e., $f \in R_{b.O}$, system \sys{} builds a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ \ret{s} $b$ or not.

\begin{figure}[tb!]
\centering
\includegraphics[width=.7\linewidth]{figures/architecture.eps}
\vspace{-1ex}
\caption{\sys{} Architecture}
\label{fig:framework}
\vspace{-2ex}
\end{figure}

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
$G_u$				& gender of user $u$				\\	\midrule
$P_u$				& province of user $u$				\\	\midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers  \\
\raisebox{1.5ex}{$R_{ee,u}$}  & over that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
$U_{t,u}$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-1ex}
\end{table}

@@

\stitle{Sina Microblog Data.} It is the data crawled to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

@@

As shown above, the distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.

>>>>

\par We consider the \retg{} behavior of users in social media.
%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.

@@

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally tweeted by $O$. Here we use 1 and 0 to denote \retd{} and  tweeted, respectively.
\end{definition}

@@

\begin{definition}
\label{def:user}
Given a user $u$, we adopt $B_u$, $R_u$ and $E_u$ to represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee is a user.
\end{definition}

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
Note that $M_b.O$ is a user, and $B_u$ is a set of microblogs.

Providing a set of users $\mathbb{U}$ and their associated microblogs $\mathbb{B}$, system \sys{} builds a \retg{} model for each group of  $\mathbb{U}$, such that given a microblog $b$ and a follower $f$ of its onwer $b.O$, i.e., $f \in R_{b.O}$, 1 or 0 is returned regarding whether $f$ \ret{s} $b$ or not.

\begin{figure}[tb!]
\centering
\includegraphics[width=.5\linewidth]{figures/architecture.eps}
\vspace{-1ex}
\caption{\sys{} Architecture}
\label{fig:framework}
\vspace{-4ex}
\end{figure}

@@

@@

\stitle{Sina Microblog Data.} It is the data crawled to be processed by \sys{}, i.e., data of microblogs and users.

@@

The distinctive feature of System  \sys{} models user \retg{} behaviors over groups instead of a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.

### 2017-12-24 DASFAA_2018/Gruba/03-fe.tex

\begin{table}[tb!]
\centering
\begin{small}
\caption{Category of User Type}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-1ex}
\end{table}

@@

With the underlying Sina Microblog Data, the Feature Extraction module is responsible for mining the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
%, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

@@

Different from the slightly straightforward \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users with their interested topics.
In short, with a given lexicon (made by some professionals) consisting of several \textit{topics}, the interest feature of a user $u$ is a normalized vector, in which each entry refers to the degree that $u$ is interested in the corresponding \textit{topic}.

@@

In system \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user $u$ versus each topic $t$ in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.

System \sys{} employs a well established lexicon to discover the explicit interests of users.
In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA \cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector \cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
We now present the detailed process for mining the interest features of a user $u$.

@@

\stitle{Step 2:} Explicit interests are explored. Specifically, every word $w$ in $WS$ is sent to match each cell word $c$ of lexicon topics.
If $w$ and $c$ are identical, $sim(w, c) = 1$, and $sim(w, c) = 0$, otherwise.
The similarity of $b$ with a lexicon topic $t$ is defined as
\begin{equation}
\label{eq:bt}
sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j).
\end{equation}

@@

If $sim(b, t)$ satisfies a certain threshold (3 by default), topic $t$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).

@@

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D_i|}{|D|}),
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single microblog $b$.

Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.

@@

\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is given by:
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t),
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.

>>>>

\begin{table}[h!]
\begin{minipage}[b]{0.6\linewidth}
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
\vspace{0.1cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
$G_u$				& gender of user $u$				\\	\midrule
$P_u$				& province of user $u$				\\	\midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of             \\	
\raisebox{1.5ex}{$R_{ee,u}$} &followers over that of followees,i.e.,$\frac{\#R_u}{\#E_u}$                  \\  \midrule
$U_{t,u}$		    & user type (as illustrated in Table \ref{tbl:ucate})      \\ \bottomrule		
\end{tabular}
\end{small}
\vspace{-1ex}
\end{minipage}
\begin{minipage}[b]{0.4\linewidth}
\centering
\begin{small}
\caption{Category of User Type}
\vspace{0.1cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and}$   \\
                        & $\ \#R_u \le 50$				  \\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-1ex}
\end{minipage}
\end{table}

@@

\par With the underlying Sina Microblog Data, the Feature Extraction module is responsible for mining the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
%, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

@@

Different from the slightly straightforward \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users with their interested topics based on their tweeted and retweeted microblogs.
In short, with a given lexicon (made by some professionals) consisting of several \textit{topics}, the interest feature of a user $u$ is a normalized vector, in which each entry refers to the degree that $u$ is interested in the corresponding \textit{topic}.

@@

In  \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user $u$ versus each topic $t$ in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.

System \sys{} employs a well established lexicon to discover the explicit interests of users.
%In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA %\cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector %\cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
When no proper explicit interests are found, two algorithms are leveraged to identify implicit interests: (1) TF-IDF (Term-Frequency and Inverse Document-Frequency) \cite{IEEEexample:books/cu/LeskovecRU14}, and (2) Twitter-LDA \cite{IEEEexample:zhao2011comparing} (a method to discover topics from Twitter, by applying the standard Latent Dirichlet Allocation (LDA) model \cite{IEEEexample:conf/jmlr/Blei03}), both of which adopt word2vector \cite{IEEEexample:mikolov2013distributed} to measure word similarity.

We now explain the detailed process for mining the interest features of a user.

@@

\stitle{Step 2:} Explicit interests are explored. Specifically, every word $w$ in $WS$ is sent to match each cell word $c$ of lexicon topics.
If $w$ and $c$ are identical, $sim(w, c) = 1$, and $sim(w, c) = 0$, otherwise.

The similarity of $b$ with a lexicon topic $t$ is defined as
\begin{equation}
\label{eq:bt}
sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j).
\end{equation}

@@

If $sim(b, t)$ satisfies a certain threshold (3 by default), topic $t$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (Definition \ref{def:inte}).

@@

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D|}{|D_i|+1}),
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $|b_i|$ appears.
Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.

@@

\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is :
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t),
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.

### 2017-12-24 DASFAA_2018/Gruba/04-uc.tex

Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
as illustrated in  Algorithm \ref{alg:uc}.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}
\begin{algorithmic}[1]
\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\vspace{1ex}
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	\State group users into $t$ clusters by $F$; \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b};
		\State out-cluster distance $d_o(u)$;
		\State Silhouette coefficient value $v(u)\ :=\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
	\EndFor
	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
\EndFor
\If {$v(a)\ =\ \ Max\{v(t)\}$} \label{opti}
	\State $R$ := $R'(a)$;
\EndIf
\State \bfseries{return} $R$.
\end{algorithmic}
\end{small}
\end{algorithm}

@@

\subsection{Clustering in \sys{}}
\label{sec:cluster}

@@

\begin{table}[tb!]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$,\\
                            &  $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$				\\	\midrule
categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_{f,u}$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors. For simplicity, we shall first illustrate the distance calculation of the simple vectors with a mono data type on each dimension, and then demonstrate that of complex vectors.

@@

>>>>

\par Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
as illustrated in  Algorithm \ref{alg:uc}.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}
\begin{algorithmic}[1]
\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\vspace{1ex}
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	%\State group users into $t$ clusters by $F$; 
    \State perform K-Gru over F to get t clusters \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b};
		\State out-cluster distance $d_o(u)$;
		\State Silhouette coefficient value $v(u)\ :=\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
	\EndFor
	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
\EndFor
\If {$v(a)\ =\ \ Max\{v(t)\}$} \label{opti}
	\State $R$ := $R'(a)$;
\EndIf
\State \bfseries{return} $R$.
\end{algorithmic}
\end{small}
\end{algorithm}

@@

\subsection{K-Gru: Clustering in \sys{}}
\label{sec:cluster}

@@

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors. For simplicity, we shall first illustrate the distance calculation of the simple vectors with a single data type on each dimension, and then demonstrate that of complex vectors.

@@

\begin{table}[tb!]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
%\vspace{0.1cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$, $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$               \\	\midrule 				
categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_u$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

### 2017-12-24 DASFAA_2018/Gruba/05-gm.tex

Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
Specifically, such model is built by the Group Modeling module for each user group and thus named as group model.
To avoid ambiguity, we shall use the term of \textit{items} to denote the data for training the group model.
A given \textit{item} is either positive or negative.

@@

	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$,\#$R_u$, \#$E_u$, $R_{ee,u}$ \}.

@@

The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to attack it.
The advantage of this classification model lies in that it could integrate different features conveniently, and
%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above.

>>>>

\par Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
Specifically, such model is built by the Group Modeling module for each user group and thus named as group model.
To avoid ambiguity, we shall use the term of \textit{items} to denote the data for training the group model.
A given \textit{item} is either positive or negative.

@@

	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$, \#$R_u$, \#$E_u$, $R_{ee,u}$\}.

@@

The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to address it. Details for random forest \cite{IEEEexample:conf/icdar/Ho1995} are omitted here for space reason.
The advantage of this classification model lies in that it could integrate different features conveniently, and
%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above.

Here we use accuracy to evaluate our model. To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$. For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0. If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0. If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0. If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0.  Formally, accuracy is defined as:

\begin{equation}
\label{eq:def-presision}
accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }.
\end{equation}
